Simple and Transparent Macroeconomic Distributional Forecasts

### 2023-10-02 presentation/presentation.tex
final presentation files

%% Beispiel-Präsentation
\documentclass[en]{sdqbeamer} 
\usepackage{graphicx}

@@

\date[28.\,9.\,2023]{September 28, 2023}

@@

\begin{columns}
\begin{column}{0.4\textwidth}
   	\begin{itemize}
         \item usual practice: issue point forecasts only
         \begin{itemize}
	    \item uncertainty is at best acknowledged, rarely quantified
	\end{itemize}
        %\item media reception often fixated on zero
        \item forecasts of different horizons are often left uncontextualized
        \item distributional forecasts supposedly would require extra modeling effort
    \end{itemize}
    \vspace{2cm}
\end{column}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\textwidth]{figures/recession_light_underlined_green_smaller_date.jpg} 
        \caption{Source: tagesschau.de}
        \label{fig:enter-label}
    \end{figure}     
\end{column}
\end{columns}
\end{frame}

\begin{frame}[t]{Contributions of this work}
\begin{itemize}
    \item show that attaching prediction intervals to an existing base of point forecasts can be 
    \begin{itemize} 
    \item simple
    \item cheap
    \end{itemize}   
    \item provide solidly performing distributional forecasts for 
    \begin{itemize}
    \item  GDP growth and inflation
    \item  all G7 countries
    \item  current and next year 
    \end{itemize}
    %\item simple and transparent method of attaching prediction intervals 
%\item show that attaching distributional forecasts to an existing
%\item for up to one and a half years into the future 
%\item evaluate on years 1999-2021
\end{itemize}
\end{frame}

@@

%\subsection{Data Source: IMF World Economic Outlook}
\begin{frame}{Data Source: IMF World Economic Outlook}
	\begin{itemize}
		\item survey by the IMF staff, published bi-annually
		\begin{itemize}
            \item contains forecasts with up to 6 years horizon and historic truth values
		    \item publication in April (horizon for current year $\approx$ 8 months) and in October ($\approx$ 2 months)
		\end{itemize}
    \item publicly available publication
    \item targets: real GDP growth and CPI inflation 
    \item available since 1990, giving $\sim$30 years of forecast-truth pairs per country and forecast horizon
    \item forecasts for G7 countries are (nearly) uninterrupted
    \begin{itemize}
        \item forecasts for 196 countries in total are available
    \end{itemize}
	\end{itemize}
\end{frame}

\section{Methods}
\begin{frame}{Methods}
We apply an attractively simple and cheap method. For a given country and target:
\begin{itemize}
    \item given forecasts $\hat{y}_{t, h}$ and the realized true values $y_{t}$ ...
    \begin{itemize}
        \item for target year $t$, horizon $h$
    \end{itemize}
    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
    \begin{itemize}
        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
        \item sets are stratified by country, target and horizon
    \end{itemize}
    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
    \item and compute the upper and lower endpoints of a central prediction interval as 
    \begin{itemize}
        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
    \end{itemize}
\end{itemize}

@@

\begin{frame}{Benchmarks}
    We compare with benchmarks:
\begin{enumerate}
    \item same methodology, alternative point forecasts
    \begin{itemize}
        \item autoregressive (AR) model
        \item Primiceri Bayesian vector autoregressive (BVAR) model
    \end{itemize}
    \item directly generated distributional forecasts
    \begin{itemize}
        \item obtained from the BVAR model
    \end{itemize}
\end{enumerate}
\begin{itemize}
    \item trained on quarterly data, with slight informational advantage
\end{itemize}

@@

\section{Results}
\begin{frame}{Scores - GDP Growth}
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

@@

\begin{frame}{Summing up}
\begin{itemize}
\item Attaching distributional forecasts via past forecast errors to an existing base of point forecasts is
    \begin{itemize}
        \item cheap
        \item competitive
        \item transparent
    \end{itemize}
\item Uncertainty around point forecasts is often substantial, making its communication necessary
\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
\item     Outlook
    \begin{itemize}
        \item employ method that ideally utilizes the cross-section dimension, e.g. via Hierarchical Bayesian Modeling
    \end{itemize}

@@

\begin{frame}{Making it public}
\textit{Refer to Shiny App}    
\end{frame}

>>>>

%% Beispiel-Präsentation
\documentclass[en]{sdqbeamer} 
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=gray,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}

@@

\date[29.\,9.\,2023]{September 29, 2023}

@@

\begin{columns}
\begin{column}{0.4\textwidth}
   	\begin{itemize}
         \item usual practice: issue point forecasts only
         \begin{itemize}
	    \item uncertainty is at best acknowledged, rarely quantified \bigskip
	\end{itemize}
        %\item media reception often fixated on zero
        \item forecasts of different horizons are often left uncontextualized \bigskip
        \item distributional forecasts supposedly would require extra modeling effort
    \end{itemize}
    \vspace{2cm}
\end{column}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\textwidth]{figures/recession_light_underlined_green_smaller_date.jpg} 
        \caption{Source: tagesschau.de}
        \label{fig:enter-label}
    \end{figure}     
\end{column}
\end{columns}
\end{frame}

\begin{frame}[t]{Contributions of this work}
\begin{itemize}
    \item show that attaching prediction intervals to an existing base of point forecasts can be 
    \begin{itemize} 
    \item simple
    \item cheap
    \item transparent
    \end{itemize}   
    \item provide competitively performing distributional forecasts for 
    \begin{itemize}
    \item  GDP growth and inflation
    \item  all G7 countries
    \item  current and next year targets
    \end{itemize}
    %\item simple and transparent method of attaching prediction intervals 
%\item show that attaching distributional forecasts to an existing
%\item for up to one and a half years into the future 
%\item evaluate on years 1999-2021
\end{itemize}
\end{frame}

@@

%\subsection{Data Source: IMF World Economic Outlook}
\begin{frame}{Data Source: IMF World Economic Outlook}
	\begin{itemize}
		\item survey by the IMF staff, published bi-annually
		\begin{itemize}
            \item contains forecasts with up to 6 years horizon and historic truth values
		    \item publication in April (horizon for current year $\approx$ 8 months) and in October ($\approx$ 2 months)
		\end{itemize}
    \item publicly available publication\footnote{International Monetary Fund. 2023. \textit{World Economic Outlook: A Rocky Recovery.} Washington, DC. April.}
    \item targets: real GDP growth and CPI inflation 
    \item time range: available since 1990, giving $\sim$30 years of forecast-truth pairs %per country and forecast horizon
    \item target locations: forecasts are issued for 196 countries in total
    %\begin{itemize}
    %    \item forecasts for 196 countries in total are available
    %\end{itemize}
	\end{itemize}
\end{frame}

\section{Methods}
\begin{frame}{Methods}
We apply an attractively simple and cheap method. For a given country and target:
\begin{itemize}
    \item given forecasts $\hat{y}_{t, h}$ and the realized true values $y_{t}$ ...
    \begin{itemize}
        \item for target year $t$, horizon $h$
    \end{itemize}
    \item ... construct sets $\mathcal{E}_{t, h} = \{\hat{e}_{t^*, h}  | t-9 \leq t^* < t \}$, containing the last nine forecast errors
    \begin{itemize}
        \item based on \textit{absolute} errors $\hat{e}_{t,h} = |y_{t} - \hat{y}_{t, h}| $
        \item sets are stratified by country, target and horizon
    \end{itemize}
    \item for $\alpha \in \{0.5, 0.8\}$, compute $q^{\alpha}_{t, h} =  Q\left(\mathcal{E}_{t, h}, \alpha \right)$
    \item and compute the upper and lower endpoints of a central prediction interval as 
    \begin{itemize}
        \item $u^{\alpha}_{t,h} = \hat{y}_{t, h} + q^{\alpha}_{t, h}$ 
        \item $l^{\alpha}_{t,h} \hspace{1mm} = \hat{y}_{t, h} - q^{\alpha}_{t, h}$
    \end{itemize}
    \item assess central interval coverage, score via the weighted interval score (WIS)\footnote{Bracher, J. et al. 2021. \textit{Evaluating
Epidemic Forecasts in an Interval Format.} PLoS Computational Biology 17 (2)}
\end{itemize}

@@

\begin{frame}{Benchmarks}
    We compare with benchmarks:
\begin{enumerate}
    \item same methodology, alternative point forecasts
    \begin{itemize}
        \item autoregressive (AR) model
        \item Primiceri Bayesian vector autoregressive (BVAR) model\footnote{Primiceri, G. 2005. \textit{Time Varying Structural Vector Autoregressions and Monetary Policy.} Review of Economic Studies 72.}
    \end{itemize}
    \item directly generated distributional forecasts
    \begin{itemize}
        \item obtained from the BVAR model
    \end{itemize}
\end{enumerate}
\begin{itemize}
    \item trained on quarterly data, with slight informational advantage
\end{itemize}

@@

\section{Results}
\begin{frame}{Scores }
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

@@

\begin{frame}{Summing up}
\begin{itemize}
\item Attaching distributional forecasts via past forecast errors to an existing base of point forecasts is
    \begin{itemize}
        \item cheap
        \item competitive
        \item transparent
    \end{itemize}
\item Uncertainty around point forecasts is often substantial, making its communication necessary
\item IMF forecasts are valuable source for distributional forecasts in their own right \bigskip \\
\item     Outlook
    \begin{itemize}
        \item scale to more countries and forecast sources
        \item implement alternative method that  utilizes the cross-section dimension%, e.g. via Hierarchical Bayesian Modeling
        \item make forecasts easily and publicly accessable via shiny app
    \end{itemize}

@@

\begin{frame}{Making it public}
\url{https://fredbec.shinyapps.io/macropi/}
\begin{columns}
\begin{column}{0.2\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/shinycap2.png}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure} 
\end{column}
\begin{column}{0.6\textwidth}
    \begin{figure}
        %\centering
        \includegraphics[width=0.7\textwidth]{figures/shinycap.jpg}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}   
\end{column}
\end{columns}
